---
title: "Find Best Logistic regression model for Adult Income Dataset"
author: "Sena Alparslan"
output: html_notebook
---


Firstly, I import data using read_csv function.
```{r}
library(readr)
dfIncome <- read_csv("/Users/Desktop/SENA/Logistic Regression/adult_income.csv")
dfIncome
```

```{r}
# Show the first few rows of the data
head(dfIncome)

colnames(dfIncome)

plot(dfIncome) 
```

```{r}
#Show attributes  
attributes(dfIncome)

# Generating a summary of all data attributes with the summary() function
summary(dfIncome)


#marital status combining
table(dfIncome$marital_status)

dfIncome$marital_status <- as.character(dfIncome$marital_status)

dfIncome$marital_status[dfIncome$marital_status == "Married-AF-spouse" |
                       dfIncome$marital_status == "Married-civ-spouse" |
                       dfIncome$marital_status == "Married-spouse-absent" ] <- "Married"

dfIncome$marital_status[dfIncome$marital_status == "Divorced" |
                       dfIncome$marital_status == "Separated" |
                       dfIncome$marital_status == "Widowed" | 
                       dfIncome$marital_status == "Never-married"] <- "Not-Married"
table(dfIncome$marital_status)




 
```
```{r}

#country combining
dfIncome$native_country <- as.character(dfIncome$native_country)

europe <- c("England", "France", "Germany", "Greece", "Holand-Netherlands",
            "Hungary", "Ireland", "Italy", "Poland", "Portugal", "Scotland",
            "Yugoslavia")
america <- c("Canada", "Cuba", "Dominican-Republic", "El-Salvador", "Guatemala",
                   "Haiti", "Honduras", "Jamaica", "Mexico", "Nicaragua",
                   "Outlying-US(Guam-USVI-etc)", "Puerto-Rico", "Trinadad&Tobago",
                   "United-States","Columbia", "Ecuador", "Peru")
asia <- c("Cambodia", "China", "Hong", "India", "Iran", "Japan", "Laos",
          "Philippines", "Taiwan", "Thailand", "Vietnam")
other <- c("South", "?")

dfIncome$native_country[dfIncome$native_country %in% america] <- "America"
dfIncome$native_country[dfIncome$native_country %in% asia] <- "Asia"
dfIncome$native_country[dfIncome$native_country %in% europe] <- "Europe"
dfIncome$native_country[dfIncome$native_country %in% other] <- "Other"

table(dfIncome$native_country)
```
```{r}
#workclass combining
table(dfIncome$workclass)

dfIncome$workclass <- as.character(dfIncome$workclass)

dfIncome$workclass[dfIncome$workclass == "Without-pay" | 
                  dfIncome$workclass == "Never-worked"] <- "Not-employe"

dfIncome$workclass[dfIncome$workclass == "State-gov" |
                  dfIncome$workclass == "Local-gov" | dfIncome$workclass == "Federal-gov" ] <- "Gov"

dfIncome$workclass[dfIncome$workclass == "Self-emp-inc" |
                  dfIncome$workclass == "Self-emp-not-inc"] <- "Self"

table(dfIncome$workclass)

# altered columns back to factors
dfIncome$native_country <- as.factor(dfIncome$native_country)
dfIncome$marital_status <- as.factor(dfIncome$marital_status)
dfIncome$workclass <- as.factor(dfIncome$workclass)
dfIncome$income_high <- as.factor(dfIncome$income_high)
str(dfIncome)

```
```{r}
#Missing Data
dfIncome[dfIncome == "?"] <- NaN

library(ggplot2)
naniar::gg_miss_var(dfIncome) +
  theme_minimal()+
  labs(y = "Missing Value") 


# correlation matrix
library(corrplot)
cor <- dfIncome[, sapply(dfIncome, is.numeric)]
cor <- cor[complete.cases(cor), ]
correlation_matrix <- cor(cor, method = "spearman")
corrplot(correlation_matrix, method="color")
```

```{r}

#split dataset
train <- dfIncome %>% sample_frac(.8)

test  <- anti_join(dfIncome, train)


# Training The Model
model1 <- glm(income_high ~ .,family = binomial(), data=train)
summary(model1)


#Prediction
prediction <- predict(model1, test, type = "response")

# Confusion Matrix
table(test$income_high, prediction >= 0.5)
```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

